Hierarchical Region-Network Sparsity for\\ High-Dimensional Inference in Brain Imaging

### 2016-02-05 paper/icml2016/example_paper.tex
add model variance results

% results: accuracy
Regarding classification performance on the identical test set,
$\ell_1$-penalized versus hierarchical-tree-penalized logistic regression
achieved
83.6\% versus 88.7\% (20\% of training data),
85.0\% versus 89.2\% (40\%),
86.8\% versus 89.8\% (60\%),
88.9\% versus 90.3\% (80\%),
88.6\% versus 89.7\% (100\%) accuracy.
% results: sparsity
Regarding model sparsity,
the measure $s = \frac{||w||_1}{||w||_F}$ was computed from
the model weights $w$ of both penalized estimators
for each of the 18 classes.
The $\ell_1$-penalized logistic regression
yielded the mean (+/- standard deviation) sparsities
50.0 (+/- 2.6), 45.4 (+/- 2.3), 40.0 (+/- 2.4), 30.9 (+/- 2.0), and 24.0 (+/- 2.3)
after model fitting with 20\% to 100\% training data.
The hierarchical-tree-penalized logistic regression
yield the sparsities
163.2 (+/- 0.7), 160.2 (+/- 1.8), 132.1 (+/- 3.3), 116.2 (+/- 4.4), and 88.4 (+/- 8.4)
after fitting 20\% to 100\% of the training data.
% results: support recovery
Finally, the support recovery was quantified by
Pearson correlation $\rho$ between vectors of
the zscored model coefficients
and
the zscored average sample maps for each class.
$\ell_1$-penalized versus hierarchical-tree-penalized logistic regression
achieved a mean correlation $\rho$ (+/- standard deviation) of
0.10 (+/- 0.03) versus 0.13 (+/- 0.04),
0.11 (+/- 0.03) versus 0.13 (+/- 0.05),
0.13 (+/- 0.04) versus 0.17 (+/- 0.05),
0.16 (+/- 0.04) versus 0.22 (+/- 0.05), and
0.19 (+/- 0.05) versus 0.29 (+/- 0.06) across classes
based on 20\% to 100\% training data.

>>>>

% results: accuracy
Regarding classification performance on the identical test set,
$\ell_1$-penalized versus hierarchical-tree-penalized logistic regression
achieved
83.6\% versus 88.7\% (20\% of training data),
85.0\% versus 89.2\% (40\%),
86.8\% versus 89.8\% (60\%),
88.9\% versus 90.3\% (80\%),
88.6\% versus 89.7\% (100\%) accuracy.
% results: sparsity
Regarding model sparsity,
the measure $s = \frac{||w||_1}{||w||_F}$ was computed from
the model weights $w$ of both penalized estimators
for each of the 18 classes.
The $\ell_1$-penalized logistic regression
yielded the mean (+/- standard deviation) sparsities
50.0 (+/- 2.6), 45.4 (+/- 2.3), 40.0 (+/- 2.4), 30.9 (+/- 2.0), and 24.0 (+/- 2.3)
after model fitting with 20\% to 100\% training data.
The hierarchical-tree-penalized logistic regression
yield the sparsities
163.2 (+/- 0.7), 160.2 (+/- 1.8), 132.1 (+/- 3.3), 116.2 (+/- 4.4), and 88.4 (+/- 8.4)
after fitting 20\% to 100\% of the training data.
% results: support recovery
Regarding the support recovery, we computed
Pearson correlation $\rho$ between vectors of
the zscored model coefficients
and
the zscored average sample maps for each class.
$\ell_1$-penalized versus hierarchical-tree-penalized logistic regression
achieved a mean correlation $\rho$ (+/- standard deviation) of
0.10 (+/- 0.03) versus 0.13 (+/- 0.04),
0.11 (+/- 0.03) versus 0.13 (+/- 0.05),
0.13 (+/- 0.04) versus 0.17 (+/- 0.05),
0.16 (+/- 0.04) versus 0.22 (+/- 0.05), and
0.19 (+/- 0.05) versus 0.29 (+/- 0.06) across classes
based on 20\% to 100\% training data.
% results: model variance
Finally, regarding model variance,
we quantified the agreement between
$\ell_1$-penalized versus hierarchical-tree-penalized
model weights after fitting
on 5 different 20\%-subsamples of the training data.
For each classifier,
the absolute model weights were concatenated for all 18 classes,
thresholded at 0.0001 to binarize variable selection,
and mutual information was computed on all pairs
of the 5 trained models.
This agreement metric of model selection across fold pairs
yielded the means 0.001 ($\ell_1$) versus 0.506 (Hierarchical Tree).
